MS Depression Paper, post replication, started 2022 09 21

### 2023-03-01 msdepression_n380_started_20230113_post_replication_just_simple_mm.Rmd
Add files via upload

@@

   Given that depression is so common in multiple sclerosis, we first wanted to check whether disease was diffuse across the brain, or whether there was network specificity (i.e. is MS random, or do MS lesions happen to strike fascicles that support the depression network, irrespective of diagnosis). To assess this, I took the following steps.

    1) Tests for normality (Shapiro–Wilk test) of proportion of disease in depression network and nondepression network. Both not normally distributed

    2) Used wilcoxon tests to compare disease (paired = T) between depression and nondepression network. As each individual contributed one measure for each network (i.e. 2 measures per person), paired was used.

@@

  Per our inclusion/exclusion criteria, we were able to identify a subset of patients that had depression, as well as a subset who did not meet criteria per EMR review. We next wanted to assess whether patients with depression had more overall disease than patients without depression.

    First, we assessed whether lesion burden (i.e. the volume occupied by white matter disease), irrespective of which fascicles were impacted, differed between patients and controls.

@@

  Next, we assessed whether fascicle burden (i.e. total volume of disease divided by total volume of all fascicles) differed between diagnostic groups.

    1) Tests for normality (Shapiro–Wilk test), fascicle burden not normally distributed.

    2) Used wilcoxon tests to compare fascicle burden between depressed and non-depressed patients. As each person only contributed one measure, paired = F.

@@

    - Disease within versus outside depression network: p = 2.2*10^-16, dep net prop = 0.400, non dep = 0.339, eff size 0.78 (large)

@@

    - Proportion Volume of whole brain fascicle disease burden: W=14996, p=0.04, dep = 0.39, nondep = 0.34, eff size 0.11 (small)

@@

    - Main effect of Network: T = 19.2, p <2 * 10^-16 (Depression Network more disease than nondepression network)

@@

@@

@@

        - Main effect of diagnosis (Depressed > Nondepressed people): T = 2.4, p = 0.048

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(boot)
library(boot.pval)
library(lsr)
library(sjPlot)
library(coin)
library(rstatix)
library(effectsize)
library(colormod)
library(ggpubr)
library(ggsignif)

@@

dep_vs_healthy_wilcoxon_lesion_volume_eff_size <- rstatix::wilcox_effsize(dep_and_healthy_groups_for_ICD_analysis, formula = volume_of_mimosa_lesions ~ depGroupVar, paired = F, conf.level = 0.95, ci.type = "perc", nboot = 1000) #eff size 0.107 (small)

@@

##### Assessing Normality w/histograms and Shapiro_Wilk test for normality ####

### Test for normality within each network, within each diagnosis

disease_overall_shapiro <- shapiro.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_per_total_network_size_sum) #W=0.97, p = 4.1 * 10^-7, NON-NORMAL

disease_dep_net_shapiro <- shapiro.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_dep_net_by_network_size_sum) #W=0.97, p = 2.0 * 10^-7, NON-NORMAL

disease_nondep_net_shapiro <- shapiro.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_nondep_net_by_network_size_sum) #W=0.97, p = 2.6 * 10^-7, NON-NORMAL

disease_dep_dx_shapiro <- shapiro.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_per_total_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]) #W=0.97, p = 0.0003 NON-NORMAL

disease_nondep_dx_shapiro <- shapiro.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_per_total_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]) #W=0.96, p = 0.0001 NON-NORMAL

## All are non-normal, will use wilcoxon for comparisons

### Within/outside depression network, V = 65897, p = 2.2*10^-16, mean dep net prop = 0.41, mean non dep = 0.31
msdisease_within_versus_outside_depression_network_sums_scaled_by_size_wilcoxon <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_dep_net_by_network_size_sum, dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_nondep_net_by_network_size_sum,paired = TRUE)

#within nondepressed group, V=9661, p <2.2*10^-16
msdisease_within_versus_outside_depression_network_nondep_group_sums_scaled_by_size_wilcoxon <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_dep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_nondep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1],paired = TRUE)

#within depressed group, V= 25143, p<2.2*10^-16
msdisease_within_versus_outside_depression_network_dep_group_sums_scaled_by_size_wilcoxon <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_dep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_nondep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2],paired = TRUE)

### Diagnostic effects

#proportion volume lost over whole network = W=14996, p=0.04, mean dep = 0.39, mean nondep = 0.34
proportion_volume_lost_over_whole_brain_dep_vs_healthy <- wilcox.test (dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_per_total_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_per_total_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], paired=FALSE)

#effsize 0.11 (small)
proportion_volume_lost_over_whole_brain_dep_vs_healthy_eff_size <- rstatix::wilcox_effsize(dep_and_healthy_groups_for_ICD_analysis, formula = proportion_volume_lost_per_total_network_size_sum ~ depGroupVar, paired = F, conf.level = 0.95, ci.type = "perc", nboot = 1000)

#proportion volume lost within depression network, W = 14969, p-value = 0.04; dep = 0.44, nondep = 0.38
proportion_volume_lost_dep_net_dep_vs_healthy <- wilcox.test (dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_dep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_dep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], paired=FALSE)

#effsize 0.11 (small)
proportion_volume_lost_over_dep_net_brain_dep_vs_healthy_eff_size <- rstatix::wilcox_effsize(dep_and_healthy_groups_for_ICD_analysis, formula = proportion_volume_lost_dep_net_by_network_size_sum ~ depGroupVar, paired = F, conf.level = 0.95, ci.type = "perc", nboot = 1000)

#proportion volume lost outside depression network W = 15134, p-value 0.051; mean dep = 0.32, mean nondep = 0.29
proportion_volume_lost_nondep_net_dep_vs_healthy <- wilcox.test (dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_nondep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_nondep_net_by_network_size_sum[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], paired=FALSE)

#effsize 0.10 (0.099) (small)
proportion_volume_lost_over_nondep_net_brain_dep_vs_healthy_eff_size <- rstatix::wilcox_effsize(dep_and_healthy_groups_for_ICD_analysis, formula = proportion_volume_lost_nondep_net_by_network_size_sum ~ depGroupVar, paired = F, conf.level = 0.95, ci.type = "perc", nboot = 1000)

@@

df_empi_dx_network_proportions <- dep_and_healthy_groups_for_ICD_analysis %>%
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = ifelse(depGroupVar==1, "MS-Depression", "MS+Depression")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Dep_network = proportion_volume_lost_dep_net_by_network_size_sum) %>%
  mutate(Nondep_network = proportion_volume_lost_nondep_net_by_network_size_sum) %>%
  dplyr::select(subject, Diagnosis, Dep_network, Nondep_network) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

#effect size within vs outside dep network, eff size = 0.78 (large)
msdisease_within_versus_outside_depression_network_sums_scaled_by_size_wilcoxon_eff_size <- rstatix::wilcox_effsize(df_empi_dx_network_proportions, formula = proportion_affected ~ Network, paired = T, conf.level = 0.95, ci.type = "perc", nboot = 1000)

#effect size dep vs nondep network within nondepressed, eff size = 0.75 (large)
msdisease_within_versus_outside_depression_network_nondep_group_sums_scaled_by_size_wilcoxon_eff_size <- rstatix::wilcox_effsize(df_empi_dx_network_proportions[(df_empi_dx_network_proportions$Diagnosis == "MS-Depression"),], formula = proportion_affected ~ Network, paired = T, conf.level = 0.95, ci.type = "perc", nboot = 1000)

#effect size dep vs dep network within depressed, eff size = 0.80, large
msdisease_within_versus_outside_depression_network_nondep_group_sums_scaled_by_size_wilcoxon_eff_size <- rstatix::wilcox_effsize(df_empi_dx_network_proportions[(df_empi_dx_network_proportions$Diagnosis == "MS+Depression"),], formula = proportion_affected ~ Network, paired = T, conf.level = 0.95, ci.type = "perc", nboot = 1000)

#diagnosis: Dep > nondep T = 2.4, p = 0.015; Network dep>nondep = T=19.2, p = 2*10^-16; intx = T = 2.3, p = 0.020
diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer)

@@

  #scale_x_discrete(labels=c("Non-depressed" = "MS-Depression", "MS+Depression" = "MS+Depression")) + 
#  ggtitle(paste0("Proportion Fascicle Volume Affected by Diagnosis")) +
  ylab("Proportion of Whole Brain White Matter Volume Affected") +
  ylim(0,0.6) + 
  theme(plot.title = element_text(size=12, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=14),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(bar_dep_vs_nondep_scaled_by_network_size) #

@@

#factor(Diagnosis, level = c('MS+Depression', 'MS-Depression'))
interaction_ggplot_bar <- ggplot(data = df_interaction_fit_upper_lower, mapping = aes(x = Diagnosis, y = model_data$predicted, color = Network,  group = interaction(Diagnosis, Network))) + 
    geom_col(position = position_dodge(width=0.6), fill = c(Network_colors_faded, Network_colors_faded), color = c(Network_colors, Network_colors), width = 0.5, size = 1.5) + 
    geom_errorbar(aes(ymin=model_data$conf.low,ymax=model_data$conf.high), position=position_dodge(width=0.6), width = 0.2,size = 1.5, color='black') +
    scale_fill_manual(values=Network_colors) + #, labels = c("MS+Depression", "MS-Depression"))+ 
    ylim(0,0.6) + 
    xlab("Diagnosis") + 
    ylab("Proportion of White Matter Network Affected") + 
    theme(axis.text.x = element_text(size=14, color="black"),
          axis.text.y = element_text(size=14, color="black"),
          axis.title.x = element_blank(), #element_text(size =16), 
          axis.title.y = element_text(size =14), 
          plot.title = element_text(size=16, hjust = 0.5),
          axis.line = element_line(size = 1.5, colour = "black", linetype=1),
          aspect.ratio = 7/5,
          panel.background = element_rect(colour = "white", fill = "white"))+

@@

diagnosis_and_interaction_bar_combined <- ggarrange(bar_dep_vs_nondep_scaled_by_network_size,interaction_ggplot_bar, 
                                                labels = c("A", "B"),
                                                font.label = list(size = 16, color = "black", family = NULL),
                                                vjust = 9,
                                                ncol = 2, nrow = 1)

print(diagnosis_and_interaction_bar_combined)
pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/diagnosis_and_intx_bargraph_range0to06.pdf"))
  diagnosis_and_interaction_bar_combined

@@

scatter_effsize_val_by_dep_net_overlap_log <- ggplot(data=df_fascicle_dep_mask_volume_overlap_effsize_value, aes(x=volume_in_dep_mask, y=dep_vs_healthy_effsize, color=dep_vs_healthy_effsize)) +
  geom_point(size=2) + 
  scale_color_gradient(low = "#FFFFFF", high = "#ff00ff") +
  geom_smooth(formula = y ~ x, method=lm, color="black")+
  scale_x_continuous(trans=scales::pseudo_log_trans(base = 10), breaks=c(0, 10, 100, 1000, 10000, 100000)) + 
  xlab("Volume of Fascicle in Depression Network") + 
  ylab("Effect Size (r)") + 
  theme(plot.title=element_text(hjust=0.5),
        axis.text = element_text(size=16, color = "black"),
        axis.title = element_text(size=18, color = "black"),
        axis.line = element_line(color="black", size=1.3),
        panel.background = element_blank(),
        legend.position = "none",
        aspect.ratio = 4/4) + 
  annotate("text", x=1.5, y=0.14, size = 5, 
           label = paste0("P = ", round(summary(dep_overlap_x_dep_vs_healthy_vol_effsize)$coef[2,4],3)))

@@

#### tertile/quintile

##### within versus outside network
#V=67727, p=2.2*10^16, top tertile prop vol affected = 0.42, bottom 2 tertiles = 0.28
msdisease_within_versus_outside_depression_network_wilcoxon_tertile <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_top_tertile_by_network_size_sum, dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_bottom_tertiles_by_network_size_sum,paired = TRUE)

#p=2.2*10^-16, top quintile prop vol affected = 0.43, bottom 4 quintiles = 0.30
msdisease_within_versus_outside_depression_network_wilcoxon_quintile <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_top_quintile_by_network_size_sum, dep_and_healthy_groups_for_ICD_analysis$proportion_volume_lost_bottom_quintiles_by_network_size_sum,paired = TRUE)

@@

@@

>>>>

#### Network, Diagnosis, and Network * Diagnosis

Model: diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)

@@

   Given that depression is so common in multiple sclerosis, we first wanted to check whether disease was diffuse across the brain, or whether there was network specificity (i.e. is MS random, or do MS lesions happen to strike fascicles that support the depression network, irrespective of diagnosis). To assess this, we looked at the main effect of network in the linear mixed model. Effect sizes were calculated with confint.

@@

  Per our inclusion/exclusion criteria, we were able to identify a subset of patients that had depression, as well as a subset who did not meet criteria per EMR review. We next wanted to assess whether patients with depression had more overall disease than patients without depression. To assess this, we looked at the main effect of diagnosis in the linear mixed model. Effect sizes were calculated with confint.

    We also assessed whether lesion burden (i.e. the volume occupied by white matter disease), irrespective of which fascicles were impacted, differed between patients and controls.

@@

#### *NetworkxDiagnosis effects: *

@@

    - Disease within versus outside depression network: p = 2.2*10^-16, dep net prop = 0.400, non dep = 0.339, eff size 0.78 (large)
     - Main effect of Network: T = 12.4, p <2 * 10^-16 (Depression Network more disease than nondepression network)

     - Main effect of network Dep > Nondep (Estimate = 0.09, 95% CI 0.076-0.104, P = 2*10^-16)

@@

    - Main effect of diagnosis MS+Depression > MS-Depression (Estimate = 0.056, 95% CI 0.011-0.100, P= 0.015)

@@

@@

    - Main effect of interaction (Estimate = 0.022, 95% CI 0.003 - 0.040, P=0.020)

@@

        - Network (.122, CI = 0.107-0.138, P < 2*10^-16)

        - Diagnosis (0.055, CI = 0.011-0.100, P = 0.015)

        - interaction (0.022, CI = 0.002-0.042, P = 0.029)

@@

        - Main effect of diagnosis (Depressed > Nondepressed people): T = 2.4, p = 0.0148)

@@

        - Network (.110, CI = 0.10-0.12, P < 2*10^-16)

        - Diagnosis (0.057, CI = 0.011-0.102, P = 0.0148)

        - interaction (0.022, CI = 0.004-0.040, P = 0.018)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(boot)
library(boot.pval)
library(lsr)
library(sjPlot)
library(coin)
library(rstatix)
#library(effectsize)
library(colormod)
library(ggpubr)
library(ggsignif)

@@

#dep_vs_healthy_wilcoxon_lesion_volume_eff_size <- rstatix::wilcox_effsize(dep_and_healthy_groups_for_ICD_analysis, formula = volume_of_mimosa_lesions ~ depGroupVar, paired = F, conf.level = 0.95, ci.type = "perc", nboot = 1000) #eff size 0.107 (small)

dep_vs_healthy_wilcoxon_lesion_volume_eff_size <- rstatix::wilcox_effsize(dep_and_healthy_groups_for_ICD_analysis, formula = volume_of_mimosa_lesions ~ depGroupVar, paired = F, conf.level = 0.95, nboot = 1000) #eff size 0.107 (small)

@@

@@

#clean up data frame
df_empi_dx_network_proportions <- dep_and_healthy_groups_for_ICD_analysis %>%
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = ifelse(depGroupVar==1, "MS-Depression", "MS+Depression")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Dep_network = proportion_volume_lost_dep_net_by_network_size_sum) %>%
  mutate(Nondep_network = proportion_volume_lost_nondep_net_by_network_size_sum) %>%
  dplyr::select(subject, Diagnosis, Dep_network, Nondep_network) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

#diagnosis: Dep > nondep T = 2.4, p = 0.015; Network dep>nondep = T=12.4, p = 2*10^-16; intx = T = 2.3, p = 0.020
diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer)

#Diagnosis: MS+ > MS- 0.011-0.1; Network dep>nondep -.104--.076; intx: -0.040--0.003
confint(diagnosis_by_network_interaction_lmer)

#Final data: 
#Main effect of network Dep > Nondep (Estimate = 0.09, 95% CI 0.076-0.104, P = 2*10^-16)
#Main effecet of diagnosis MS+Depression > MS-Depression (Estimate = 0.056, 95% CI 0.011-0.100, P= 0.015)
#Main effect of interaction (Estimate = 0.022, 95% CI 0.003 - 0.040, P=0.020)

@@

  #scale_x_discrete(labels=c("Non-depressed" = "MS-Depression", "MS+Depression" = "MS+Depression")) + 
#  ggtitle(paste0("Proportion Fascicle Volume Affected by Diagnosis")) +
  ylab("Proportion of Whole Brain White Matter Affected") +
  ylim(0,0.6) + 
  theme(plot.title = element_text(size=12, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=14),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(bar_dep_vs_nondep_scaled_by_network_size) #

@@

#factor(Diagnosis, level = c('MS+Depression', 'MS-Depression'))
interaction_ggplot_bar <- ggplot(data = df_interaction_fit_upper_lower, mapping = aes(x = Diagnosis, y = model_data$predicted, color = Network,  group = interaction(Diagnosis, Network))) + 
    geom_col(position = position_dodge(width=0.6), fill = c(Network_colors_faded, Network_colors_faded), color = c(Network_colors, Network_colors), width = 0.5, size = 1.5) + 
    geom_errorbar(aes(ymin=model_data$conf.low,ymax=model_data$conf.high), position=position_dodge(width=0.6), width = 0.2,size = 1.5, color='black') +
    scale_fill_manual(values=Network_colors) + #, labels = c("MS+Depression", "MS-Depression"))+ 
    ylim(0,0.6) + 
    xlab("Diagnosis") + 
    ylab("Proportion of White Matter Network Affected") + 
    theme(axis.text.x = element_text(size=14, color="black"),
          axis.text.y = element_text(size=14, color="black"),
          axis.title.x = element_blank(), #element_text(size =16), 
          axis.title.y = element_text(size =14), 
          plot.title = element_text(size=16, hjust = 0.5),
          axis.line = element_line(size = 1.5, colour = "black", linetype=1),
          aspect.ratio = 7/5,
          panel.background = element_rect(colour = "white", fill = "white")) +

@@

diagnosis_and_interaction_bar_combined <- ggarrange(bar_dep_vs_nondep_scaled_by_network_size,interaction_ggplot_bar, 
                                                labels = c("A", "B"),
                                                font.label = list(size = 16, color = "black", family = NULL),
                                                vjust = 7,
                                                ncol = 2, nrow = 1)

print(diagnosis_and_interaction_bar_combined)
ggsave(plot = diagnosis_and_interaction_bar_combined, filename =paste0(homedir, "/results/Figures_for_msdepression_paper/diagnosis_and_intx_bargraph_range0to06.pdf"), height = 8, width = 9)
#pdf(file=paste0(homedir, "/results/Figures_for_msdepression_paper/diagnosis_and_intx_bargraph_range0to06.pdf"))
 # diagnosis_and_interaction_bar_combined
#dev.off()

@@

scatter_effsize_val_by_dep_net_overlap_log <- ggplot(data=df_fascicle_dep_mask_volume_overlap_effsize_value, aes(x=volume_in_dep_mask, y=dep_vs_healthy_effsize, color=dep_vs_healthy_effsize)) +
  geom_point(size=2) + 
  scale_color_gradient(low = "#FFFFFF", high = "#ff00ff") +
  geom_smooth(formula = y ~ x, method=lm, color="black")+
  scale_x_continuous(trans=scales::pseudo_log_trans(base = 10), breaks=c(0, 10, 100, 1000, 10000, 100000)) + 
  xlab("Volume of Fascicle in Depression Network") + 
  ylab("Effect Size (r)") + 
  theme(plot.title=element_text(hjust=0.5),
        axis.text = element_text(size=16, color = "black"),
        axis.title = element_text(size=18, color = "black"),
        axis.line = element_line(color="black", size=1.3),
        panel.background = element_blank(),
        legend.position = "none",
        aspect.ratio = 4/4) + 
  annotate("text", x=1.6, y=0.14, size = 5, 
           label = paste0("P = ", round(summary(dep_overlap_x_dep_vs_healthy_vol_effsize)$coef[2,4],2)))

@@

@@

confint(diagnosis_by_network_interaction_lmer_tertile)

#Final for tertiles
#Network (.122, CI = 0.107-0.138, P < 2*10^-16)
#Diagnosis (0.055, CI = 0.011-0.100, P = 0.015)
#interaction (0.022, CI = 0.002-0.042, P = 0.029)

@@

confint(diagnosis_by_network_interaction_lmer_quintile)

#Final for quintile
#Network (.110, CI = 0.10-0.12, P < 2*10^-16)
#Diagnosis (0.057, CI = 0.011-0.102, P = 0.0148)
#interaction (0.022, CI = 0.004-0.040, P = 0.018)
